Between Subgraph Isomorphism and Maximum Common Subgraph

### 2017-01-31 poster/poster.tex
initial redraft - text cut, figures improved

The \textbf{non-induced subgraph isomorphism problem} is to find an injective mapping from a given
pattern graph to a given target graph which preserves adjacency---in essence, we are ``finding a
copy of'' the pattern inside the target.

@@

Despite these problems being \NP-complete, modern practical subgraph isomorphism algorithms can
handle problem instances with many hundreds of vertices in the pattern graph, and up to \textbf{ten thousand
vertices} in the target graph, leading to successful application in areas such as \textbf{computer
vision}, \textbf{biochemistry}, and \textbf{pattern recognition}.
}

@@

The maximum common subgraph problem is much more difficult in practice than subgraph isomorphism.
The state of the art for the maximum common subgraph
problem becomes \textbf{computationally
infeasible at only 35 vertices} when working with
unlabelled graphs. This is largely because strong inference,
based upon the degrees of vertices and the
distances or paths between them, is possible with subgraph isomorphism,
but not maximum common subgraph, and so the
state space in the former is much more restricted, whilst filtering
during search is vastly stronger.}

@@

If $k$ is reasonably small, weakened forms of invariants from subgraph isomorphism (based on vertex degrees and paths) are still effective at reducing the search space.  In the example it is clear that the pattern graph is not isomorphism to a subgraph of the target, but upon removal of the central vertex we have a $1$-less isomorphism from the pattern to the target.

@@

Are there instances for which k = 0 is unsatisfiable, but that
are satisfiable for small k? For the problem families which
do not consist entirely of satisfiable instances, we plot this for both the induced and non-induced variants.

@@

In the ``phase'' family, which consists of instances
crafted to be extremely difficult to solve, we are not able
to answer this question, and in the ``scalefree'' family we
see no satisfiable instances with low but not zero k. 
However, in several of the remaining families our algorithm manages to more than double
the number of instances for which exact solutions are
known, and we gain upper bounds on many more. This is particularly
interesting for the ``images-CVIU11'', where the size of the solution has a
direct \textbf{real-world interpretation} in terms of \textbf{closeness of image
matching}.

@@

\begin{wrapfigure}[11]{r}{0.66\linewidth}
\begin{center}
\input{gen-graph-runtimes}
\end{center}
\end{wrapfigure}
What would happen if we used the $k$-less approach to solve the
maximum common induced problem? We could simply start
at k = 0, and increase k until a solution is found. This \textbf{tackles the problem in the opposite direction from existing
approaches}, which work by attempting to construct
larger and larger solutions. In the figure, ``$k\downarrow$'' is our algorithm, whilst ``FC'' and
``clique'' are state of the art maximum common subgraph algorithms.

@@

We see that \textbf{our approach is able to close over twice
as many of these instances as the previous state of the art} --- which struggles due to it's RAM requirements.
(The same conclusion holds even if every instance which is
satisfiable with k = 0 is removed from the dataset.)
On instances designed for the maximum subgraph problem we are still the single strongest solver, and our performace is complementary to that of the clique encoding. 
}
\begin{columns}
\column{0.5}

\block{See the Paper For\ldots}{
    \begin{itemize}
        \item ~ Description of our new invariants, and proofs that they hold. 
        \item ~ Description of the algorithm the algorithm.
    \end{itemize}
}

@@

{
    \colorlet{blockbodybgcolor}{uofgsandstone!80!white}
    \colorlet{blocktitlebgcolor}{uofgsandstone!80!white}
    \block[bodyverticalshift=-0.5cm]{}{
        This work was supported by the Engineering and Physical Sciences Research Council [grant
        numbers EP/K503058/1 and EP/M506539/1]. \hfill \texttt{\textcolor{white}{c.mccreesh.1@research.gla.ac.uk}}
    }
}

>>>>

The \textbf{non-induced subgraph isomorphism problem} is to find an injective mapping from a given
pattern graph to a given target graph which preserves adjacency.

@@

Despite these problems being \NP-complete, modern practical subgraph isomorphism algorithms can
handle problem instances with many hundreds of vertices in the pattern graph, and up to \textbf{ten thousand
vertices} in the target graph, leading to successful application in areas such as \textbf{computer
vision}, \textbf{malware detection}, \textbf{compilers}, \textbf{model checking}, \textbf{biochemistry}, and \textbf{pattern recognition}.
}

@@

The maximum common subgraph problem is much more difficult in practice than subgraph isomorphism.
The state of the art for the maximum common subgraph
problem becomes \textbf{computationally
infeasible at only 35 vertices} when working with
unlabelled graphs. This is largely because strong inference,
based upon the degrees of vertices and the
distances or paths between them, is possible with subgraph isomorphism,
but not maximum common subgraph.}

@@

If $k$ is reasonably small, weakened forms of invariants from subgraph isomorphism (based on vertex degrees and paths) are still effective at reducing the search space.  In the example, upon removal of the central vertex from the pattern, we have a $1$-less isomorphism from the pattern to the target.

@@

Are there instances for which $k = 0$ is unsatisfiable, but that
are satisfiable for small $k$? For the problem families which
do not consist entirely of satisfiable instances, we plot this for both the induced and non-induced variants.

@@

In the ``phase'' family, which consists of instances
crafted to be extremely difficult to solve, we are not able
to answer this question, and in the ``scalefree'' family we
see no satisfiable instances with low but not zero $k$.

However, in several of the remaining families our algorithm manages to provide exact solutions for many instances. This is particularly
interesting for the ``images-CVIU11'', where the size of the solution has a
direct \textbf{real-world interpretation} in terms of \textbf{closeness of image
matching}.

@@

\begin{wrapfigure}[11]{r}{0.66\linewidth}
\begin{center}
\input{gen-graph-runtimes}
\end{center}
\end{wrapfigure}
What would happen if we used the $k$-less approach to solve the
maximum common induced problem? We could simply start
at $k = 0$, and increase $k$ until a solution is found. This \textbf{tackles the problem in the opposite direction to existing
approaches}, which work by attempting to construct
larger and larger solutions. In the figure, ``$k\downarrow$'' is our algorithm, whilst ``FC'' and
``clique'' are state of the art maximum common subgraph algorithms.

@@

We see that \textbf{our approach is able to close over twice
as many of these instances as the previous state of the art}---which struggles due to its RAM requirements.
On instances designed for the maximum subgraph problem we are still the \newline single strongest solver.
}
\begin{columns}
\column{0.5}

\block{See the Paper for\ldots}{
    \begin{itemize}
        \item ~ Description of our new invariants, and proofs that they hold. 
        \item ~ Description of the algorithm.
    \end{itemize}
}

@@

{
    \colorlet{blockbodybgcolor}{uofgsandstone!80!white}
    \colorlet{blocktitlebgcolor}{uofgsandstone!80!white}
    \block[bodyverticalshift=-0.5cm]{}{
        This work was supported by the Engineering and Physical Sciences Research Council [grant
        numbers EP/K503058/1 and EP/M506539/1]. \hfill \texttt{\textcolor{white}{c.reilly.2@research.gla.ac.uk}}
    }
}
